\begin{CV}
    \jobentry{Jul 2018}{Dec 2018}
        {Software Engineer}
        {Syndeck}{https://synwave.co/}{Savosa, Ticino, Switzerland}
        {Developed a bluetooth gateway application (in Go) that handles the communication with various
        medical devices. Analyzed and implemented various protocols, first in Python, then in Go.
        Contributed to the Node.JS / TypeScript codebase and implemented the types for the communication 
        between the platforms with Protobuf.}
    \jobentry{Nov 2014}{Oct 2017}{Head of IT Department / Co-Founder}
        {Coelis}{https://coelis.ch/}{Lugano, Ticino, Switzerland}
        {Started a startup at the age of 18, with the goal of providing engineering solutions to our clients problems.
        During my time in Coelis I've extended \href{https://github.com/invoiceplane}{Invoiceplane}'s project to handle
        medical invoices, so that our clients (mainly physiotherapists) could use this tool as a service to ease their 
        invoicing workflow. 
        I've integrated the \href{http://sumex1.net/}{Sumex1} invoice generator module by creating 
        a C\# app that handled the XML request that were sent via a REST API, so that the invoicing generation could be 
        performed directly from the webapp. The changes were then commited and merged into the existing open source 
        project and we began selling the service. \\
        In addition to this project, during my time in Coelis I've handled all the server management works,
        developed several websites, designed a couple of logos / corporate identities, implemented our whole
        infrastructure (Git, Jenkins, ownCloud, Docker, Postfix, Dovecot, nginx), managed our own CA and provided 
        customer support to our clients.}
    \jobentry{Nov 2015}{Aug 2016}
    {Civil Service - Administrative help}{Fondazione Opera Charitas}
    {http://charitas.ch/}{Lugano, Switzerland}{During my mandatory Civil Service, I've worked at Fondazione Opera 
        Charitas to provide some administrative help.
        Because of my IT background, I've also had the opporunity to help them manage their IT infrastructure 
        by providing technical support and developing some useful tools.\\
        During this time I've developed a software for an embedded device connected to a touch screen and a 
        POS printer (Citizen CT-S801), that was placed in their kitchen and used to
        print receipts for every meal prepared by the cooks of the structure.
        I've also developed an Android app that was intended to run on a kiosk device 
        (a Google Pixel C enclosed in a kiosk structure) to let the employees to pay and reserve their meal
        with the company's badge (LEGIC RFID badges / Mifare DESFire badges) at the canteen. This solution was
        developed to provide a cashless payment system in the infrastructure. \\
        This app was also integrated with the existing cafeteria software and the 
        \textit{PrintReceipts} software that is running in the kitchen's embedded computer.}
\end{CV}