\begin{CV}

    \projectentry{Aug 2017}{Today}{Linux on Pixel C}{https://github.com/denysvitali/linux-on-pixel-c}
    {}
    {linux}
    {With this ongoing project, we're offering a solution to replace Android and use any GNU/Linux distro 
    on the \href{https://en.wikipedia.org/wiki/Pixel_C}{Google Pixel C}, a tablet made by Google powerd by an NVIDIA Tegra X1 SoC.
    This project also helped / received help from the \href{https://reswitched.team/}{Reswitched Team} for the 
    \href{https://github.com/denysvitali/linux-on-pixel-c/issues/1}{Green bars issue} which subsequently allowed to
    some users to push the required patches upstream and expand the project to 
    \href{https://github.com/fail0verflow/switch-linux}{other devices} / 
    \href{https://github.com/postmarketOS/pmbootstrap/pull/1534}{other projects}.}

    %\projectentry{Feb 2019}{Today}{TSP Cup 2019}{https://github.com/denysvitali/tsp-cup-2019}
    %{}
    %{java}
    %{A Traveling Salesman Problem solver, written in Java, using the following algorithms:
    %\begin{itemize}
    %    \item Simulated Annealing
    %    \item Ant Colony Optimization
    %    \item Genetic Algorithm (w/ EAX)
    %    \item Nearest Neighbor
    %    \item Random Nearest Neighbor
    %\end{itemize}}

    
    %\projectentry{Feb 2019}{Today}{TSP Node Server}{https://github.com/denysvitali/tsp-node-server}
    %{}
    %{go,postgres}
    %{A Go REST server to collect the requests from different TSP Solver Nodes. This project was used 
    %as a server to the 30+ clients running a custom-made Alpine Linux distribution that ran my TSP Solver for
    %about 2 days, so that all the results could be collected in a PostgreSQL database.}

    \projectentry{Jul 2018}{Today}{DMS.rs}{https://github.com/DMSrs/dmsrs}
    {}
    {rust, postgres, html5, css3, js}
    {A Document Management System, written in Rust. This tools allows its users to upload some PDFs of previously
    scanned documents, run an OCR and save the resulting text in a DB for further indexing. PostgreSQL was used as a
    backend DB.}

    %\projectentry{Feb 2019}{Today}{paper-fix}{https://github.com/DMSrs/paper-fix}
    %{}
    %{cpp}
    %{An image deskewer, to fix the perspective of scanned documents (e.g: when they're scanned with a mobile phone)}


    %\projectentry{Nov 2018}{May 2018}{Tuna}{https://github.com/denysvitali/tuna}
    %{}
    %{cpp}
    %{A graphics engine and GUI written in C++ with VR capabilities, reflection, Blinn-Phong, LeapMotion integration.
    %Developed during the coruses of \textit{Computer Graphics} and \textit{Virtual Reality} at SUPSI.}
    

    %\projectentry{Oct 2018}{Jan 2019}{iFunny}{https://github.com/denysvitali/ifunny}
    %{}
    %{java}
    %{An interpreter of a custom language (funny) written in Java. Developed during the 
    %\textit{Compilers and Interpreters} course at SUPSI.}
    
    %\projectentry[2em]{Aug 2018}{Aug 2018}{go-against-humanity}{https://github.com/ESCah/go-against-humanity}
    %{}
    %{go}
    %{An interactive, web-based, multi-player, Card Against Humanity game implementation. Written for fun with
    %a friend at \href{https://www.endsummercamp.org}{End Summer Camp 2018}.}
    

    \projectentry{Mar 2018}{Today}{OptiTravel}{https://github.com/denysvitali/optitravel}
    {}
    {java}
    {A journey planner that uses \textit{gtfs-server} and \textit{TransitLand} to find the best route, by using
    public transportation services. The routing is done on the client side with the A* algorithm.\\
    This project, developed in Java with JavaFX, was developed during the Software Engineering I course
    at the University of Applied Sciences of Southern Switzerland during my bachelor,
    with two other people.}

    
    \projectentry{Mar 2018}{Today}{gtfs-server}{https://github.com/denysvitali/gtfs-server}
    {}
    {rust,postgres}
    {General Transit Feed Specification (GTFS) REST server, which provides some GIS functionnalities provided
    by the PostgreSQL backend. This project was developed alongside \textit{OptiTravel}.
    This project was developed entirely by myself as an addition to the \textit{OptiTravel} project.}


    \projectentry{Dec 2017}{Today}{nginx-error-pages}{https://github.com/denysvitali/nginx-error-pages}
    {}
    {html5,css3}
    {This project provides some nice-looking error pages for NGINX web server.}
    
    %\projectentry{Oct 2017}{Jan 2018}{viz-fgk-compressor}{https://github.com/denysvitali/viz-fgk-compressor}
    %{}
    %{c}
    %{An Adaptive Huffman FGK compressor / decompressor, written in C for the course 
    %\textit{Algorithms and Data Structures} at SUPSI.}

    \pagebreak

    \projectentry{Mar 2016}{Today}{Sonos-Web}{https://github.com/denysvitali/sonos-web}{}{html5, css3, js}
    {Web Interface for the \href{https://sonos.com/}{Sonos Audio System}, created with the goal of having a
    nice looking UI to manage the playing queue, add streaming services like YouTube and Spotify, and allow
    other developers to customize the UX as they want by making the project expandable through the use of plugins.}
    
    \projectentry{May 2016}{Today}{The Best Mother*** Website}{https://github.com/denysvitali/thebestmotherfuckingwebsite}
    {https://thebestmotherfucking.website/}
    {html5,css3}
    {Satire website to joke on the fact that a website doesn't need any framework to look cool.}
    
    %\projectentry[2em]{Jun 2015}{Oct 2016}{nodegram-bot}{https://github.com/denysvitali/nodegram-bot}{}
    %{nodejs}
    %{A Telegram-bot written in Node.JS, customizable, extendible and modular with the use of plugins.}


    \projectsbanner
    
    
\end{CV}